---
title: "Compiling Italian Lexical Lookup Database for ConversationAlign_IT"
author: "Jamie Reilly, Anna Borghi, Claudia Mazzucca, Marc Brysbaert, Marco Marelli, Chiara Fini, Davide Crepaldi, Vanessa Era, Giovanna Cuomo"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 1
    css: "https://github.com/Reilly-ConceptsCognitionLab/reillylab_publicdata/blob/main/jr_20.css?raw=true"
---

```{r setup, include=F}
knitr::opts_chunk$set(fig.width=8, fig.height=5, fig.align = 'left', fig.path='Figs/', cache.path='Cache/', eval=T, echo=T, tidy=TRUE,  cache=F, message=F, warning=F, stringsAsFactors=F, yaml.eval.expr = TRUE)  

library(xfun)
pkg_attach("tidyverse", "here", "kableExtra", "RCurl", "knitr", "RColorBrewer", 'broom', 'purrr', 'textstem', 'tibble', 'quanteda', 'tidyr',  'quanteda.textstats', install=T)

jamie.theme <- theme_bw() + theme(axis.line = element_line(colour = "black"), panel.grid.minor = element_blank(), panel.grid.major = element_blank(), panel.border = element_blank(), panel.background = element_blank(), legend.title= element_blank())  #custom theme ggplot2


print.me <- function(x, ...) {
if (nrow(x) > 200){
   len <- 200 
    } else {
       len <- (nrow(x))
}
   x[1:len,] %>%
   kbl(digits=2, align= 'l', booktabs=T) %>%
   kable_styling(fixed_thead = T) %>%
   kable_paper("striped", full_width = T, html_font = "Helvetica", font_size = 11) %>%
   row_spec(0, color = "white", background = "#5b705f", font_size = 12) %>%
   scroll_box(width = "700px", height = "500px") %>%
   asis_output()
}

registerS3method("knit_print", "data.frame", print.me)
```

# Overview
Our goal is to compile a lexical lookup database that contains many Italian words characterized across many formal and semantic dimensions. We need a lookup database that is light enough to be bundled within an R package but comprehensive enough to provide decent coverage across any language sample (i.e., dyadic conversation transcripts). <br>

# Questions to resolve
1. Naming conventions (e.g., phon_nletters, HumanOnly, LLM_Augmented) <br>

# Base Dictionary
We will compile a lookup database for Italian by first building on: <br>
[Amenta et al (2025) The Italian Crowdsourcing Project: Visual word recognition times for 130,495 Italian words. Behavior Research Methods.]
(https://link.springer.com/article/10.3758/s13428-024-02548-4)

# Format the original dictionary
1. Eliminated duplicates <br>
2. to lowercase <br>
3. Omitted first few entries (bound morphemes/suffixes marked by hyphens) <br>
4. Save as RDA (optimize compression format) <br>
5. Post to github
```{r, eval=F}
#read in lightly formatted dictionary data
base_lookup <- read.csv('~/Library/CloudStorage/OneDrive-TempleUniversity/Reilly_RData/ConversationAlign_IT (dev)/data/Italian_LookupBase_Prepped26.csv')
base_lookup <- data.frame(word=tolower(base_lookup$word))
str(base_lookup)

#Are there any duplicates? - Yes there are six duplicates in the original database. 
#sum(duplicated(base_lookup$word))

#Kill duplicates (take only first entry)
base_lookup <- base_lookup %>% dplyr::distinct(word, .keep_all = TRUE) 

#Check no dplicates
sum(duplicated(base_lookup$word))

#Save as RDA optimizing file compression, post on github 
save(base_lookup, file='data/base_lookup.rda', compress='xz')

```

# Load base Italian entires 
Read in formatted base lookup from github
```{r}

```


# Append nletts and order dat
Using base R count letters in each word, order lookup word first, then order cols alphabetical by prefix
```{r}
#compute new var and order it second in the dataframe
dat <- dat %>% dplyr::mutate(base_nlett = nchar(word)) %>% relocate(base_nlett, .after = 1)  
colnames(dat)
lex_lookup25 <- dat
str(lex_lookup25)
```

# Save output as rda and cvs for posting
```{r, eval=T}
write.csv(lex_lookup25, file='lookup_databases/lex_lookup25.csv')
save(lex_lookup25, file='lookup_databases/lex_lookup25.rda')
```





